---
title: "Module 11 - Integer Programming"
author: "Avinash Ravipudi"
date: "2022-11-17"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

AP shipping company's problem formulation: 

//OBJECTIVE FUNCTION
MIN: 775X1 + 800X2 + 800X3 + 800X4 + 800X5 + 775X6 + 750X7;

// CONSTRAINS
WORKERS REQUIRED ON SUNDAY  CONSTRAINTS : X2 + X3 + X4 + X5 + X6 >= 18;
WORKERS REQUIRED ON MONDAY  CONSTRAINTS : X3 + X4 + X5 + X6 + X7 >= 27;
WORKERS REQUIRED ON TUESDAY  CONSTRAINTS : X1 + X4 + X5 + X6 + X7 >= 22;
WORKERS REQUIRED ON WEDNESDAY  CONSTRAINTS : X1 + X2 + X5+ X6 + X7 >= 26;
WORKERS REQUIRED ON THURSDAY  CONSTRAINTS : X1 + X2 + X3 + X6 + X7 >= 25;
WORKERS REQUIRED ON FRIDAY  CONSTRAINTS : X1 + X2 + X3 + X4 + X7 + >= 21;
WORKERS REQUIRED ON SATURDAY  CONSTRAINTS : X1 + X2 + X3 + X4 + X5 >= 19;

// INTEGERS X1,X2,X3,X4,X5,X6,X7>=0 ;

X1 : workers assigned for shift 1 = 2;
X2 : workers assigned for shift 2 = 4;
X3 : workers assigned for shift 3 = 5;
X4 : workers assigned for shift 4 = 0;
X5 : workers assigned for shift 5 = 8;
X6 : workers assigned for shift 6 = 1;
X7 : workers assigned for shift 7 = 13;

*Reading the lp file:*
```{r}
library(lpSolveAPI)
AP_Shipping <- read.lp("shipping.lp")
AP_Shipping
```
*lp model solution:*
```{r}
solve(AP_Shipping) #Optimal solution found
```
*How much did everything cost in total?*
```{r}
get.objective(AP_Shipping)  #The minimum wage expense is $25,675
```
*How many staff are accessible each day?*
```{r}
get.variables(AP_Shipping) 
```
*The number of workers available for each shift is as follows:*
```{r}
workers <- matrix(c(0,4,5,0,8,1,0,
                    0,0,5,0,8,1,13,
                    2,0,0,0,8,1,13,
                    2,4,0,0,8,1,13,
                    2,4,5,0,0,1,13,
                    2,3,4,0,0,0,13,
                    2,4,5,0,8,0,0), ncol=7,byrow=TRUE)
row.names(workers) <- c('SUN','MON','TUE','WED','THUR','FRI','SAT')
colnames(workers)<- c('SHIFT-1','SHIFT-2','SHIFT-3','SHIFT-4','SHIFT-5','SHIFT-6','SHIFT-7')
workers
```
*The number of workers needed each day to reduce total wage expenses:*
```{r}
rowSums(workers)
```


