---
title: "Goal Programming"
author: "Avinash Ravipudi"
date: "2022-11-04"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
EMAX Corporation:

Maximize Z = P - 6C - 3D, where  
               
             P = total (discounted) profit over the life of the new products, 
             C = change (in either direction) in the current level of employment, 
             D = decrease (if any) in next year’s earnings from the current year’s level.

From the Given table i can write an equation as follows

        P = 20X1 + 15X2 + 25X3
       Y1 = 6X1 + 4X2 + 5X3 - 50
       Y2 = 8X1 + 7X2 +5X3 - 75

         Y1+ is going over the employment level goal and the weighted penality is 6
         Y1- is going under the employment level goal and the weighted penality is 6
         Y2+ is going over the earnings goal for next year- no penality
         Y2- is going under the earnings goal for next year and the peanlity is 3.
         X1 is the quantity of product 1 to be produced
         X2 is the quantity of product 2 to be produced
         X3 is the quantity of product 3 to be produced 


LP formulation:
__________________
// Objective function
MAX: 20X1 + 15X2 + 25X3 - 6 Y1P - 6 Y1M - 3 Y2M;

// Constraints
6X1 + 4X2 + 5X3 + Y1P - Y1M = 50;
8X1 + 7X2 + 5X3 + Y2P - Y2M = 75;

```{r}
library(lpSolveAPI)
Zmax <- read.lp("Zmax.lp")
Zmax
```


```{r}
solve (Zmax)
```

```{r}
get.objective(Zmax)
```

```{r}
#To make 225 million dollars, Emax must create 15 units of product 3 and none of products 1 and 2. Employment will exceed the target by 2500 people.
get.variables(Zmax)
```
